\documentclass[eng]{class}

% Publication Title
\title{EDI: First/Second Lab Report}
% Short title for the header (copy the main title if it is not too long)
\shorttitle{EDI: First/Second Lab Report}
       
% Authors
\author[1]{D. Ligari 518592}
% Author Affiliations
\affil[1]{University of Pavia, Department of Computer Engineering (Data Science), Pavia, Italy}
% Surname of the first author of the manuscript
\firstauthor{Ligari}
%Contact Author Information
\contactauthor{D. Ligari} % Name and surname of the contact author
\email{davide.ligari01@universitadipavia.it} % Contact Author Email
% Publication data (will be defined in the edition)
\publicationdate{\today}
% Place your particular definitions here
\newcommand{\vect}[1]{\mathbf{#1}}  % vectors


\abstract{  This report presents two analyses of network performance with regards to ProtonVPN servers and DNS servers.
The first analysis evaluates the performance of various ProtonVPN servers and investigates the impact of server location on network performance.
To accomplish this, measurements of latency, packet loss, and network bandwidth were taken using tools such as Speedtest-cli, Ping, and MTR.
The second analysis focuses on DNS performance, beginning with an overview of DNS functionality
and studying the contents of DNS queries and responses, followed by an evaluation of the performance of different DNS servers and protocols.\\
During the investigation, the latency, packet loss, and DNS query resolution time of different DNS servers was measured.
The results provide insights into optimal server selection to maximize performance, privacy and security of the user.}
\keywords{
  VPN • Performance • Speedtest • Ping • MTR • DNS • dig • dnseval • DNSSEC • DoT • DoH}
\date{\today}
% Start document
\begin{document}
\pagenumbering{arabic}
% Include title, authors, abstract, etc.
\maketitle
\tableofcontents
\thispagestyle{FirstPage}
\section{Web technologies}
\subsection*{Analyze and discuss the impacts of the number of parallel connections set inside the browser
  on the Page Load Times of commercial/institutional websites. Did you notice any expected or
  unexpected behavior?}

\pagestyle{OtherPage}

\subsection*{Analyze and discuss the impacts of caching policies implemented by different
  commercial/institutional websites on the Page Load Times. Consider websites that support
  HTTP/1.1, HTTP/2 and HTTP/3 (possibly with unsecure and secure connections). Did you notice
  any expected or unexpected behavior?}


\subsection*{Analyze and discuss the performance of different commercial/institutional websites obtained
  under different conditions using the ab – Apache HTTP server benchmarking tool. Did you
  notice any expected or unexpected behavior?}

\subsection*{Analyze and discuss the performance of different commercial/institutional websites obtained
  under different conditions using the nghttp and h2load tools. In the experiments with
  h2load analyze the role of the warm-up time. Did you notice any expected or unexpected
  behavior?}


\section{Conclusions}

\end{document}