\documentclass[eng]{class}
% Publication Title
\title{Movie Reviews: A machine learning project}
% Short title for the header (copy the main title if it is not too long)
\shorttitle{Movie Reviews}
       
% Authors
\author[1]{D. Ligari 518592}
% Author Affiliations
\affil[1]{University of Pavia, Department of Computer Engineering (Data Science), Pavia, Italy}
% Surname of the first author of the manuscript
\firstauthor{Ligari}
%Contact Author Information
\contactauthor{D. Ligari} % Name and surname of the contact author
\email{davide.ligari01@universitadipavia.it} % Contact Author Email
% Publication data (will be defined in the edition)
\publicationdate{\today}
% Place your particular definitions here
\newcommand{\vect}[1]{\mathbf{#1}}  % vectors

\abstract{ 
  This report provides a comprehensive analysis of the steps taken to develop a machine learning model for classifying film reviews. 
  The dataset used in this study is Andrew Maas's \textit{Large Movie Review Dataset}, which includes 50,000 labelled film reviews as either positive or negative.
  Prior to training the model, a preprocessing phase was conducted, which involved creating a vocabulary consisting of all words in the dataset,
  and a bag-of-words (BOW) approach where the number of occurrences of each word in each review was counted. 
  The BOW approach was subsequently used to train the model.
  Different models were then created and compared, 
  incorporating various preprocessing techniques, including stemming and the removal of common and meaningless words from the vocabulary. 
  The report also includes the use of different classifiers, such as logistic regression and multinomial Naive Bayes. 
  }
\keywords{ Machine Learning • Classification • Sentiment Analysis • Logistic Regression • Multinomial Naive Bayes}
\date{\today}
% Start document
\begin{document}
% Include title, authors, abstract, etc.
\maketitle
\thispagestyle{FirstPage}
%Figures and tables must be cited in the text and explained in detail. Do not forget to add a caption to each figure/table/
\section{Introduction}
\firstword{I}{n}
recent years, the exponential growth of digital media and the internet has led to an unprecedented amount of content being produced and consumed on a daily basis.
One of the most popular forms of digital media is film, with millions of reviews available online from a variety of sources. With this vast amount of data available,
it has become increasingly challenging to manually process and classify this information.
By using large datasets and advanced algorithms, machine learning models can accurately classify reviews based on their content.
In this report, is presented a thorough analysis of the steps taken to create a machine learning model for classifying film reviews.

\end{document}